### 2023-10-26 main.tex
s
ll
Compact formulas
l

\subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
By knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
\begin{equation}\label{ABS-vect}
    |\Psi^{'}\rangle =\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
\begin{equation}\label{ABS}
			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
	%\com{Double check this. Sum looks strange}
%and where
% \begin{equation}\label{CiEquation}
%	c_{y}=\begin{cases}
%		1\quad \text{if}\quad \tau_{y}\neq 1\\
%		0\quad \text{if}\quad \tau_{y}=1
%	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. \\ \\
\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites. We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$. Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$. It follows that we have
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
Observing that
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
we finally obtain 
	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

>>>>

\begin{equation}
\begin{split}
\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\\
% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
\end{split}
\end{equation}
The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.

Looks like there is a mistake somewhere...
}
\subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
By knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
\begin{equation}\label{ABS-vect}
    |\Psi^{'}\rangle =\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
\end{equation}
where  
\begin{equation}\label{ABS}
		\begin{split}
			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
		\end{split}
	\end{equation} 
	%\com{Double check this. Sum looks strange}
%and where
% \begin{equation}\label{CiEquation}
%	c_{y}=\begin{cases}
%		1\quad \text{if}\quad \tau_{y}\neq 1\\
%		0\quad \text{if}\quad \tau_{y}=1
%	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
%\end{equation}
\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. \\ \\
\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites. We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as
\begin{align}
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
\end{align}
For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
\begin{equation}
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt
\end{equation}
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$. Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$. It follows that we have
\begin{equation}
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
\end{equation} 
Observing that
\begin{equation}
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
\end{equation}
we finally obtain 
\begin{equation}\label{PsiI-N2}
	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
\end{equation}
